The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2023-02-06 src/tex/article.tex
usetex back to True
added minor suggestions from coauthors

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (\edit1{three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} }), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, 
%
\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon. The difference between these models lies in the assumptions in the underlying empirical galaxy relations. In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities. }
% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
%
\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies), 
and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
}
% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
%
\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}. Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies. 
}

>>>>

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (\edit1{three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} }), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, 
%
\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon. The difference between these models lies in the assumptions in the underlying empirical galaxy relations. In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities. }
% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
%
\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies), 
and a local galaxy mass-metallicity relation as in \cite{PettiniPagel2004}. 
This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. 
Assuming that starburst galaxies follow the empirical fundamental metallicity relation (leading to anti-correlation between the SFR and metallicity), their inclusion tends to shift the peak of \SFRDzZ to
lower metallicities and broadens the low-metallicity part of the distribution.
}
% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
%
\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function where the slope for the low-mass end is constant over redshift, and a local galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}. Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies. 
}
